Powdery Milder yield loss mitigation strategies in Mungbean a Meta-analysis

### 2019-08-29 index.Rmd
Update after meeting with Adam
Reordered research questions

What is the length of a Mungbean season and how has it varied in this trial

@@

>>>>

@@

What is the length of a Mungbean season and how has it varied in this trial.  
   - This data has not been collected or is not accuarate enough to be useful to answer this question.

## parts fof analysis that need checking

Variability among host genotypes and probable influence of season given that over the years, the genotype studied changed from Berken, Crystal to Jade.
